What is long-distance dispersal? And a taxonomy of dispersal events\\ \vspace{2cm}

### 2016-10-09 Manuscript/MS- What is LDD.tex
Fixed Acknowldg.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Acknowledgements
\emph{Acknowledgements}. I am indebted to Cristina García, José A. Godoy, Manolo Carrión, Juan Luis García-Castaño, Jesús Rodríguez and, especially, Juan Miguel Arroyo for generous help with field and laboratory work and making possible this study. I appreciate the help and advice of Cristina García and Etienne Klein during the final stages of the manuscript. The study was supported by a Junta de Andalucía Excellence Grant (RNM-5731), as well as a Severo Ochoa Excellence Award from the Ministerio de Economía y Competitividad (SEV-2012-0262). The Agencia de Medio Ambiente, Junta de Andalucía, provided generous facilities that made possible this study in the Andalusian natural parks (Sierra de Cazorla, Alcornocales) and authorized my work there.

>>>>

LDD, and its variation across coexisting plant species, could also have far-reaching consequences for community assembly and forest physiognomy. Yet very few previous analyses addressed this point. Comparative information on LDD across species sharing a common environment have found strong differences in LDD potential among plants with different (e.g. Clark et al. 1999 Ecology; Martínez et al. 2008 Oecologia) or even with the same dispersal syndrome (e.g. García et al. 2016 Basic Applied Ecology).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Acknowledgements
\emph{Acknowledgements}. I am indebted to Cristina García, José A. Godoy, Manolo Carrión, Juan Luis García-Castaño, Jesús Rodríguez and, especially, Juan Miguel Arroyo for generous help with field and laboratory work and making possible this study. I appreciate the help and advice of Cristina García and Etienne Klein during the final stages of the manuscript. The study was supported by a Junta de Andalucía Excellence Grant (RNM-5731), as well as a Severo Ochoa Excellence Award from the Ministerio de Economía y Competitividad (SEV-2012-0262) and CGL2013-47429P grant. The Consejería de Medio Ambiente, Junta de Andalucía, provided generous facilities that made possible this study in the Andalusian natural parks (Sierra de Cazorla, Alcornocales) and authorized my work there.
